Coherent IR-Hyper-Raman Four Wave Mixing Vibrational Spectroscopy

### 2024-07-27 paper.tex
Update paper.tex

\subsection{Electronically Non-resonant}
Assuming $\omega_2$, $\omega_3$ are significantly detuned from any resonance (\autoref{fig:comparisonwmel}),\cite{Placzek1934, Long1970, Altmann1982} \autoref{sivegamma} is written as 
When there is no electronic resonance, HDFG has also been referred to as singly vibrationally enhanced (SIVE) spectroscopy. \cite{RN352}
We first investigate the HDFG selection rules through a Placzek type formalism.
Contracting over the virtual states forms the hyper-Raman hyperpolarizability $\beta$.\cite{Long1970} 
\begin{equation}\label{sivebeta}
	\gamma_{ijkl}^{vg} =	-\frac{1}{\varepsilon_0} \frac{1}{4D \hbar}\frac{\beta^{vg}_{ijk} \mu^{gv}_{l}}{\Delta_{gv}} \rho_{gg}
\end{equation}
All infrared active transitions are hyper-Raman active, making HDFG allowed for any infrared active transition. \cite{Andrews1978}
This selection rule is generally valid for any HDFG when $\omega_2$ and $\omega_3$ are sufficiently detuned from any resonance.
% It is important to note that the symmetry properties of $\beta_{ijk}$ change dependent upon whether $\omega_2$ and $\omega_3$ are degenerate. \cite{Denisov1986, Kozich2007}  
% DDK: not important, I think?  does this have any bearing on our analysis?

The formula gets simpler when we consider IR excitation of a normal mode.  
Assume $\omega_1$ is tune to the $n^{\text{th}}$ reduced normal mode.
Taylor expanding the dipole and first hyperpolarizability operators in terms of an $n^{\text{th}}$ reduced normal mode coordinate $Q_n$ to $\order{Q_n}$ about equilibrium as\cite{Long1970, Shen90}
\begin{subequations}
	\begin{equation}
		\mu_l = \mu_{l,0} + \left(\frac{\partial \mu_l}{\partial Q_n}\right)_0 Q_n 
	\end{equation}
	\begin{equation}
		\beta_{ijk} = \beta_{ijk,0} + \left(\frac{\partial \beta_{ijk}}{\partial Q_n}\right)_0 Q_n
	\end{equation}
\end{subequations}
and substituting into \autoref{sivebeta} gives the HDFG hyperpolarizability to $\order{Q_n}$ as \begin{equation}\label{SIVEselection}
	\gamma_{ijkl}^{vg} =	-\frac{1}{\varepsilon_0} \frac{1}{8D m_n \omega_{vg}}  \frac{1}{{\Delta_{gv}}} \ \left(\frac{\partial \beta^{vg}_{ijk}}{\partial Q_n}\right)_0 \left({\frac{\partial \mu^{gv}_{l}}{\partial Q_n}}\right)_0  \rho_{gg}
\end{equation}
% DDK: do we call m_n the reduced mass, or the effective mass?
where we have used $\mel{n}{Q_n}{g} = \sqrt{\frac{\hbar}{2m_n\omega_{ng}}}$, $m_n$ is the reduced mass of the normal mode and $\omega_{ng}$ is the characteristic frequency.\cite{RN230}
Since this expression is non-zero in the harmonic oscillator limit, HDFG output is allowed for normal modes in the harmonic limit.

@@

\subsection{Electronically resonant and pre-resonant}

While Placzek treatment provides the general source of HDFG output, it does not predict the behavior of $\beta_{ijk}$ as $\omega_2 + \omega_3$ is changed.
We now explicitly consider electronic resonances through the $A,B,C$ decomposition of $\beta$ introduced by Chung and Ziegler, analogous to those found in Albrecht's treatment of Raman spectroscopy.\cite{Albrecht1961, Ziegler1988} 
To employ this formalism, we write the states in a Born-Oppenheimer basis $\ket{a,b}$, where $\ket{a,b} = |a(Q)) \otimes \ket{b}$ for electronic states $\{|a(Q))\}$ and vibrational states $\{\ket{b}\}$ (i.e., adiabatic approximation). \cite{BornOppenheimer, Tang1970}
The dependence of the electronic states on the adiabatic parameter $Q$ is suppressed for simplicity.
% DDK: can label with fig:comparisonwmel if desired
% The states are labeled as shown in \autoref{fig:hdfg}.
For consistency with previous reports, we use $\vec{R}$ to denote electric transition dipole moments; $\vec{\mu}$ is reserved for transitions on the ground electronic state. \cite{Tang1970}
Following the approach which gave \autoref{sivegamma}, we find
\begin{equation}\label{drgamma_notaylor}
	\gamma_{ijkl} = -\frac{1}{\varepsilon_0} \frac{1}{4D \hbar^3} \sum_{m,n,e,v'} \frac{
		R_{i}^{gv, ev'} 
		R_{j}^{ev',mn} 
		R_{k}^{mn,g0} 
		R_{l}^{g0,gv} 
	}{\Delta_{g0,gv}
		\Delta_{ev', mn}
		\Delta_{mn, g0}
	}
\end{equation}
where $R_{i}^{ab,cd}$ is the i$^{th}$ element of $\mel{a,b}{\vec{R}}{c,d}$.
It is common in the hyper-Raman community to write $\Delta_{ev', mn} \Delta_{mn, g0} = \Delta_{ev', g0}$.
Using our definition of vibronic states, we can write, for example,
$R_{i}^{gv,ev'} = \mel{v}{M_i^{ge}}{v'}$.
Expanding $\vec{M}^{ij}$ to $\order{Q}$ about the equilibrium point of the ground state potential surface as
$\vec{M}^{ij} = \vec{M}^{ij}_0 + \sum_z \frac{\partial\vec{M}^{ij}}{\partial Q_z} Q_z$
yields $A, B, C$ coefficients similar to those in the Albrecht formalism of Raman scattering, \cite{Albrecht1961, Ziegler1988} so that
\begin{equation}
		\gamma_{ijkl} \sim \left(A_{ijk} + B_{ijk} + C_{ijk}\right) \frac{\mel{v}{\mu_{l}}{0}} {\Delta_{g0,gv}}
\end{equation}
The $A$ term contains the static transitions (i.e., Condon approximation), the $B$ term depends upon $\order{Q}$ transitions (Herzberg-Teller contributions), and the $C$ term depends on $\order{Q^2}$ transitions. 
The C term is suppressed in the following discussion as it depends on one and two photon forbidden transitions, making its contribution to $\gamma_{ijkl}$ two orders of magnitude lesser than $A_{ijk}$. \cite{Ziegler1988, Neddersen1989, Bonang1992}
Note that some reports obtain $A, B$ coefficients through a Herzberg-Teller expansion of the electronic states to expose vibronic couplings via $\partial H / \partial Q$, where H is the electronic Hamiltonian.\cite{HerzbergTeller1933, Petrov1985, Neddersen1989, Baranov1990}
This approach is not used here as the expansion of $\vec{M}^{ij}$ in normal mode coordinates provides sufficient physical insight into hyper-Raman selection rules.

By contracting over the virtual vibrational states $\ket{n}$, the $A$ and $B$ coefficients, where $B = B_1 + B_2$, are written as
\begin{widetext}
\begin{subequations}\label{ABterms}
\begin{equation}
	\begin{split}
		A_{ijk} = \frac{1}{\hbar^2}\sum_{m,e,v'} M^{ge}_{0,i} 
		M^{em}_{0,j} 
		M^{mg}_{0,k}
		 \langle v | v' \rangle
		 \langle v' | 0 \rangle 
		 \frac{1}{\Delta_{ev', g0}}
		 \\
	\end{split}
\end{equation}
	\begin{equation}
		\begin{split}
			B_{1_{ijk}} &= \frac{1}{\hbar^2} \sum_{m,e,v',z} M^{ge}_{0,i} \langle v | v' \rangle \left(
			 \frac{\partial M^{em}_{j}}{\partial Q_z} M^{mg}_{0,k} \mel{v'}{Q_z}{0} 
			+M^{em}_{0,j} \frac{\partial M^{mg}_{k}}{\partial Q_z} \mel{v'}{Q_z}{0} \right) \frac{1}{\Delta_{ev', g0}}\\
		\end{split}
	\end{equation}
	\begin{equation}
	\begin{split}
			B_{2_{ijk}} = \frac{1}{\hbar^2} \sum_{m,e,v',z} \frac{\partial M^{ge}_{i}}{\partial Q_z} M^{em}_{0,j} 
			M^{mg}_{0,k} \mel{v}{Q_z}{v'} 
			\langle v' | 0 \rangle 
			\frac{1}{\Delta_{ev', g0}}
	\end{split}
	\end{equation}
\end{subequations}
\end{widetext}
where terms such as $\langle a | b \rangle$ and $\mel{a}{Q}{b}$ are Franck-Condon factors and Herzberg-Teller-type integrals, respectively. 
These expressions are valid for both singly and doubly resonant HDFG, but based upon the resonance schemes, further simplifications can be made (\textit{vide infra}).

The selection rules for HDFG can be made clearer by small manipulations of \autoref{ABterms}. 
%HDFG (where a vibrational and vibronic state are resonantly coupled) can provide a tool for measuring vibronic coupling, analogous to fully resonant DFG. \cite{Dick83_1, Shen94}
% Many multi-resonant nonlinear spectroscopies have been developed to resolve vibronic coupling in molecular samples. \cite{Carlson1990, Gaynor2017, RN276}
% HDFG provides methods to investigate vibronic coupling with only two laser pulses.
% HDFG experiment selectively excites quanta in ground state vibrational modes, making it similar to a stimulated hyper-Raman experiment. 
% As a result, the spectrum along the electronic scanning axis ($\omega_2 + \omega_3$) is significantly simplified as the coupling between the vibronic states are isolated to only $\ket{g,0}$ and $\ket{g,1}$, assuming the infrared pulse puts a single quantum in the normal mode of interest ($\ket{g,1}$).
By working only in terms of a single normal mode (i.e. removing the sum over $z$ and $v=1$) and assuming electronic transitions occur only between $|g), |e)$, 
% $v' = \{0,1,2\}$, 
the A and B terms are rewritten as 
	\begin{subequations}\label{ABterms_DR}
		\begin{equation}
			\begin{split}
				A_{ijk} = \frac{1}{\hbar}\sum_{v'} M^{ge}_{0,i} 
				\Lambda^{eg}_{0,jk}
				\langle 1 | v' \rangle
				\langle v' | 0 \rangle 
				\frac{1}{\Delta_{ev',g0}}
				\\
			\end{split}
		\end{equation}
		\begin{equation}
			\begin{split}
				B_{1_{ijk}} &= \frac{1}{\hbar} \sum_{v'} M^{ge}_{0,i} \langle 1 | v' \rangle 
				\frac{\partial \Lambda^{eg}_{jk}}{\partial Q} \mel{v'}{Q}{0} 
				\frac{1}{\Delta_{ev', g0}}\\
			\end{split}
		\end{equation}
		\begin{equation}
			\begin{split}
				B_{2_{ijk}} = \frac{1}{\hbar} \sum_{v'} \frac{\partial M^{ge}_{i}}{\partial Q} 
				\Lambda^{eg}_{0,jk} 
				\mel{1}{Q}{v'} 
				\langle v' | 0 \rangle 
				\frac{1}{\Delta_{ev',g0}}
			\end{split}
		\end{equation}
	\end{subequations}
where the electronic two photon absorption operator, $\Lambda$ was invoked to simplify summation over virtual states. \cite{McClain1977}
The constraint of $v' = \{0,1,2\}$ is done for simplicity.

The selection rules for DR-HDFG follow more clearly from \autoref{ABterms_DR}.
It is clear from \autoref{ABterms_DR} that the Condon approximation breaks down for centrosymmetric molecules, as inversion centers invoke strict parity constraints that make states not accessible via both one and two photon transitions. \cite{Milojevich2013, RN230}
This makes DR-HDFG a unique tool for studying the electronic structure of centrosymmetric species in isotropic media, as it is sensitive to non-Condon effects. \cite{Olson2018}
The $B_1$ and $B_2$ terms involve different types of vibronic coupling pathways.
In $B_1$, the Herzberg-Teller coupling is associated with the two-photon absorption process, whereas in $B_2$, the Herzberg-Teller coupling is associated with one-photon emission.
As such, $B_1$ contributions to a DR-HDFG spectrum will be sensitive to vibronic coupling between the ground state of a mode and vibrational states on the $|e)$ surface. 
$B_2$ contributions are sensitive to vibronic coupling between the first excited state of a mode $\ket{g,1}$ and vibrational states on $|e)$.

\begin{figure*}[!htbp]
	\centering
	\includegraphics[width=6.66in]{drsive_spectrum.png}
	\caption{Contributions of $A, B$ (\autoref{ABterms_DR}) to DR-HDFG spectrum for a simple two harmonic well system.
		(a) Potential energy surfaces for a two-well system, (b) 1D HDFG spectrum for $\xi = 0.5$, $\omega_1 = \omega_{g1, g0}$. 
		It is assumed that $\omega_2 = \omega_3$.
		Note that (b) plots magnitudes of the labeled quantities.
		The vibrational states on the $|g)$ and $|e)$ manifolds are spaced 2200 cm$^{-1}$ apart, with the vibronic states $\ket{e,v'}$ given linewidths of 700 cm$^{-1}$ and $\hbar \omega_{eg}$ = 30000 cm$^{-1}$.
		Dotted lines in (b) denote the $v'$ = 0, 1, 2 vibronic resonances. 
		The vibronic one and two photon absorption operators are scaled such that $\abs{B}/\abs{A} \sim$ 0.1, following Chung and Ziegler. \cite{Ziegler1988}}
	\label{fig:doubres_spec}
\end{figure*}

The impact of vibronic coupling in the 2D spectrum is made clear by using a simple model. \cite{Kundu2022}
Using a two-well system described by 
\begin{subequations}
	\begin{equation}
		H_g = \frac{p^2}{2m} + \frac{1}{2} \hbar \omega q^2
	\end{equation}
and
	\begin{equation}
		H_e = \frac{p^2}{2m} + \frac{1}{2} \hbar \omega (q-\xi)^2 +\hbar \omega_{eg}
	\end{equation}
\end{subequations}
for the ground ($H_g$) and first excited ($H_e$) states, where $p$ is the momentum of the normal mode, the A and B contributions can be evaluated using Franck-Condon and Herzberg-Teller integrals tabulated in terms of the dimensionless normal mode $q$ and offset parameter $\xi$ (\autoref{fig:doubres_spec}a). \cite{Carlson1988thesis} 
Note that $q = \sqrt{\frac{m^2\omega}{\hbar}} Q$.
The spectrum is simulated for an electronic state which is both one and two photon allowed.
A simulated spectrum   (\autoref{fig:doubres_spec}b) highlighting the contributions of these terms on potential wells with $\xi = 0.5$ dissects the $A$ and $B$ contributions to the DR-HDFG spectrum.
This stimulated hyper-Raman type spectrum would be the expected result in a DR-HDFG experiment when investigating the vibronic structure of the electronic state coupled to $\ket{g,v}$.

Simulating the DR-HDFG spectrum for the simple two-well system allows dissection of selection rules and spectral signatures without the need for complex couplings.
There are two relevant regions of interest: the resonant region (2$\omega_2$ $\in$ [29000, 35000] cm$^{-1}$) and the non-resonant region.
Focusing far away from the resonant region ($2\omega_2 \sim$ 20000 cm$^{-1}$), the nonresonant $A$ term response is roughly equivalent to that of the resonant $B$ term response. 
Previous reports suggest that $A$ term contributions may become negligible when significantly detuned from a resonance such that $\Delta_{ev', g0} \approx \Delta_{eg}$, i.e., the resonance denominator loses $\ket{v'}$ dependence. \cite{Neddersen1989}
The lack of $\ket{v'}$ dependence in the resonance denominator causes $A$ to vanish through closure ($A_{ijk} \sim \sum_{v'} \langle 1|v' \rangle \langle v'|0\rangle$ = $\delta_{10} = 0$).
However, the simulated spectrum (\autoref{fig:doubres_spec}b) shows a non-negligible $A$ contribution to DR-HDFG output well beyond $\sim$ 20000 cm$^{-1}$, the limit for this model system where $\abs{\omega_{ev',g0} - 2\omega_2} \gg 2\Gamma_{ev',g0}$.
As such, it is difficult to eliminate $A$ term resonances in HDFG spectra, even when largely detuned ($\gg 2\Gamma_{ev',g0}$) from the electronic state. 
Similar ideas have been seen in spontaneous Raman scattering. \cite{Li1990, Gong2015}
As such, it may prove difficult to examine non-Condon effects in DR-HDFG spectra of noncentrosymmetric systems.

@@

\section{Applications of HDFG}\label{quant}
% DDK: the problem is "applications" does not fit well into the story we have framed in the intro.  
% DDK: what about "comparisons of HDFG with other spectroscopies"?
% also, can some of these things really be called applications?  is site-selectivity an application?  is turning a v-SFG measurement into a HDFG measurement an application?
\subsection{Site Selectivity}
Unlike resonant hyper-Raman spectroscopy, which allows transitions between different normal modes of varying quanta, the infrared pulse in the HDFG provides a type of site selectivity,\cite{RN103, Carlson1991} so that only the mode pumped by $\omega_1$ can be involved in vibronic coupling.  
% DDK: I kind of understand this point...but a hyper-Raman spectrum would clearly select the vibrational mode based on the Raman shift, correct?
%  good to note the benefits of this technique compared to hyper-Raman:
% - a form of stimulated hyper-Raman (=stronger, directional signals)
% - experiment takes place over a short time window, so pump-probe experiments are easily implemented
% - laser scatter is easily avoided
% - IR active, not 
HDFG methods should be able to supplement older coherent Raman based methods as a method to investigate vibronic coupling mechanisms between a specific vibration on the ground state and vibrational states on an arbitrary excited state.\cite{RN103}
The combined infrared and hyper-Raman properties of HDFG make it highly sensitive to molecular electronic structure.
Particularly in the case of a centrosymmetric species, non-Condon effects dominate in the spectrum as the $A$ term vanishes from the presence of an inversion center.
The site selective properties of HDFG can allow for parsing of non-Condon effects in different vibrational modes, and extend the use of CMDS to understand the electronic and vibronic structure of simple and complex species.

>>>>

% DDK: or should this be "Vibrational Selection Rules"?  Does Placzek == nonresonant?
\subsection{Electronically Non-resonant: Vibrational Selection Rules}
When $\omega_2+\omega_3$ is significantly detuned from resonance,\cite{Placzek1934, Long1970, Altmann1982} \autoref{sivegamma} 
% DDK: broken thought here
When there is no electronic resonance, HDFG has also been referred to as singly vibrationally enhanced (SIVE) spectroscopy. \cite{RN352}
We first investigate the HDFG selection rules through a Placzek type formalism.
Contracting over the virtual states forms the hyper-Raman hyperpolarizability $\beta$:\cite{Long1970} 
\begin{equation}\label{sivebeta}
	\gamma_{ijkl}^{vg} =	-\frac{1}{\varepsilon_0} \frac{1}{4D \hbar}\frac{\beta^{vg}_{ijk} \mu^{gv}_{l}}{\Delta_{gv}} \rho_{gg}.
\end{equation}
All infrared active transitions are hyper-Raman active, making HDFG allowed for any infrared active transition. \cite{Andrews1978}
This selection rule is generally valid for any HDFG when $\omega_2$ and $\omega_3$ are sufficiently detuned from any resonance.
% It is important to note that the symmetry properties of $\beta_{ijk}$ change dependent upon whether $\omega_2$ and $\omega_3$ are degenerate. \cite{Denisov1986, Kozich2007}  
% DDK: not important, I think?  does this have any bearing on our analysis?

The formula gets simpler when we consider IR excitation of a normal mode.  
Assume state $v$ is the $n^{\text{th}}$ reduced normal mode.
We Taylor expand the dipole and first hyperpolarizability operators to first order in the reduced normal mode coordinate $Q_n$ about equilibrium:\cite{Long1970, Shen90}
\begin{subequations}
	\begin{equation}
		\mu_l = \mu_{l,0} + \left(\frac{\partial \mu_l}{\partial Q_n}\right)_0 Q_n 
	\end{equation}
	\begin{equation}
		\beta_{ijk} = \beta_{ijk,0} + \left(\frac{\partial \beta_{ijk}}{\partial Q_n}\right)_0 Q_n
	\end{equation}
\end{subequations}
Substituting into \autoref{sivebeta} gives the HDFG hyperpolarizability to $\order{Q_n}$ as \begin{equation}\label{SIVEselection}
	\gamma_{ijkl}^{vg} =	-\frac{1}{\varepsilon_0} \frac{1}{8D m_n \omega_{vg}}  \frac{1}{{\Delta_{gv}}} \ \left(\frac{\partial \beta^{vg}_{ijk}}{\partial Q_n}\right)_0 \left({\frac{\partial \mu^{gv}_{l}}{\partial Q_n}}\right)_0  \rho_{gg}
\end{equation}
% DDK: do we call m_n the reduced mass, or the effective mass?
where we have used $\mel{v}{Q_n}{g} = \sqrt{\frac{\hbar}{2m_n\omega_{ng}}}$, $m_n$ is the reduced mass of the normal mode, and $\omega_{ng}$ is the characteristic frequency.\cite{RN230}
Since this expression is non-zero in the harmonic oscillator limit, HDFG output is allowed for normal modes in the harmonic limit.

@@

\subsection{Electronically resonant and pre-resonant: Vibronic Selection Rules}
% TODO: note that the IR dipole selection rule persists here--this is all about w2+w3 resonance

While the Placzek treatment provides the general source of HDFG output, it does not predict the behavior of $\beta_{ijk}$ as $\omega_2 + \omega_3$ is changed.
We now explicitly consider electronic resonances through the $A,B,C$ decomposition of $\beta$ introduced by Chung and Ziegler, analogous to those found in Albrecht's treatment of Raman spectroscopy.\cite{Albrecht1961, Ziegler1988} 
To employ this formalism, we write the states in a Born-Oppenheimer basis $\ket{a,b}$, where $\ket{a,b} = |a(Q)) \otimes \ket{b}$ for electronic states $\{|a(Q))\}$ and vibrational states $\{\ket{b}\}$ (i.e., adiabatic approximation). \cite{BornOppenheimer, Tang1970}
We will henceforth suppress the dependence of the electronic states on $Q$ for simplicity.
% DDK: can label with fig:comparisonwmel if desired
% The states are labeled as shown in \autoref{fig:hdfg}.
For consistency with previous reports, we use $\vec{R}$ to denote electric transition dipole moments; $\vec{\mu}$ is reserved for transitions on the ground electronic state. \cite{Tang1970}
Following the approach which gave \autoref{sivegamma}, we find
\begin{equation}\label{drgamma_notaylor}
	\gamma_{ijkl} = -\frac{1}{\varepsilon_0} \frac{1}{4D \hbar^3} \sum_{m,n,e,v'} \frac{
		R_{i}^{gv, ev'} 
		R_{j}^{ev',mn} 
		R_{k}^{mn,g0} 
		R_{l}^{g0,gv} 
	}{\Delta_{g0,gv}
		\Delta_{ev', mn}
		\Delta_{mn, g0}
	}
\end{equation}
where $R_{i}^{ab,cd}$ is the i$^{th}$ element of $\mel{a,b}{\vec{R}}{c,d}$.
It is common in the hyper-Raman community to write $\Delta_{ev', mn} \Delta_{mn, g0} = \Delta_{ev', g0}$.
Using our definition of vibronic states, we can write, for example,
$R_{i}^{gv,ev'} = \mel{v}{M_i^{ge}}{v'}$.
Expanding $\vec{M}^{ij}$ to $\order{Q}$ about the equilibrium point of the ground state potential surface as
$\vec{M}^{ij} = \vec{M}^{ij}_0 + \sum_z \frac{\partial\vec{M}^{ij}}{\partial Q_z} Q_z$
yields $A, B, C$ coefficients similar to those in the Albrecht formalism of Raman scattering, \cite{Albrecht1961, Ziegler1988} so that
\begin{equation}
		\gamma_{ijkl} \sim \left(A_{ijk} + B_{ijk} + C_{ijk}\right) \frac{\mel{v}{\mu_{l}}{0}} {\Delta_{g0,gv}}
\end{equation}
The $A$ term contains the static transitions (i.e., Condon approximation), the $B$ term depends upon $\order{Q}$ transitions (Herzberg-Teller contributions), and the $C$ term depends on $\order{Q^2}$ transitions. 
The C term is suppressed in the following discussion as it depends on one and two photon forbidden transitions, making its contribution to $\gamma_{ijkl}$ two orders of magnitude lesser than $A_{ijk}$. \cite{Ziegler1988, Neddersen1989, Bonang1992}
Note that some reports obtain $A, B$ coefficients through a Herzberg-Teller expansion of the electronic states to expose vibronic couplings via $\partial H / \partial Q$, where H is the electronic Hamiltonian.\cite{HerzbergTeller1933, Petrov1985, Neddersen1989, Baranov1990}
This approach is not used here as the expansion of $\vec{M}^{ij}$ in normal mode coordinates provides sufficient physical insight into hyper-Raman selection rules.

% By contracting over the virtual vibrational states $\ket{n}$, 
The $A$ and $B$ coefficients, where $B = B_1 + B_2$, are written as:
\begin{widetext}
\begin{subequations}\label{ABterms}
\begin{equation}
	\begin{split}
		A_{ijk} = \frac{1}{\hbar^2}\sum_{m,e,v'} M^{ge}_{0,i} 
		M^{em}_{0,j} 
		M^{mg}_{0,k}
		 \langle v | v' \rangle
		 \langle v' | 0 \rangle 
		 \frac{1}{\Delta_{ev', g0}}
		 \\
	\end{split}
\end{equation}
	\begin{equation}
		\begin{split}
			B_{1_{ijk}} &= \frac{1}{\hbar^2} \sum_{m,e,v',z} M^{ge}_{0,i} \langle v | v' \rangle \left(
			 \frac{\partial M^{em}_{j}}{\partial Q_z} M^{mg}_{0,k} \mel{v'}{Q_z}{0} 
			+M^{em}_{0,j} \frac{\partial M^{mg}_{k}}{\partial Q_z} \mel{v'}{Q_z}{0} \right) \frac{1}{\Delta_{ev', g0}}\\
		\end{split}
	\end{equation}
	\begin{equation}
	\begin{split}
			B_{2_{ijk}} = \frac{1}{\hbar^2} \sum_{m,e,v',z} \frac{\partial M^{ge}_{i}}{\partial Q_z} M^{em}_{0,j} 
			M^{mg}_{0,k} \mel{v}{Q_z}{v'} 
			\langle v' | 0 \rangle 
			\frac{1}{\Delta_{ev', g0}}
	\end{split}
	\end{equation}
\end{subequations}
\end{widetext}
where terms such as $\langle a | b \rangle$ and $\mel{a}{Q}{b}$ are Franck-Condon factors and Herzberg-Teller-type integrals, respectively. 
At this point, the expressions are valid for both electronically resonant and non-resonant cases.

For the case of electronic resonance, further simplifications can be made.
We restrict consideration to electronic transitions between $|g)$ and $|e)$.  
% The selection rules for HDFG can be made clearer by small manipulations of \autoref{ABterms}. 
%HDFG (where a vibrational and vibronic state are resonantly coupled) can provide a tool for measuring vibronic coupling, analogous to fully resonant DFG. \cite{Dick83_1, Shen94}
% Many multi-resonant nonlinear spectroscopies have been developed to resolve vibronic coupling in molecular samples. \cite{Carlson1990, Gaynor2017, RN276}
% HDFG provides methods to investigate vibronic coupling with only two laser pulses.
% HDFG experiment selectively excites quanta in ground state vibrational modes, making it similar to a stimulated hyper-Raman experiment. 
% As a result, the spectrum along the electronic scanning axis ($\omega_2 + \omega_3$) is significantly simplified as the coupling between the vibronic states are isolated to only $\ket{g,0}$ and $\ket{g,1}$, assuming the infrared pulse puts a single quantum in the normal mode of interest ($\ket{g,1}$).
By working only in terms of a single normal mode (i.e. removing the sum over $z$ and $v=1$), 
% $v' = \{0,1,2\}$, 
the A and B terms are rewritten as 
	\begin{subequations}\label{ABterms_DR}
		\begin{equation}
			\begin{split}
				A_{ijk} = \frac{1}{\hbar}\sum_{v'} M^{ge}_{0,i} 
				\Lambda^{eg}_{0,jk}
				\langle 1 | v' \rangle
				\langle v' | 0 \rangle 
				\frac{1}{\Delta_{ev',g0}}
				\\
			\end{split}
		\end{equation}
		\begin{equation}
			\begin{split}
				B_{1_{ijk}} &= \frac{1}{\hbar} \sum_{v'} M^{ge}_{0,i} \langle 1 | v' \rangle 
				\frac{\partial \Lambda^{eg}_{jk}}{\partial Q} \mel{v'}{Q}{0} 
				\frac{1}{\Delta_{ev', g0}}\\
			\end{split}
		\end{equation}
		\begin{equation}
			\begin{split}
				B_{2_{ijk}} = \frac{1}{\hbar} \sum_{v'} \frac{\partial M^{ge}_{i}}{\partial Q} 
				\Lambda^{eg}_{0,jk} 
				\mel{1}{Q}{v'} 
				\langle v' | 0 \rangle 
				\frac{1}{\Delta_{ev',g0}}
			\end{split}
		\end{equation}
	\end{subequations}
% DDK: give Lambda an explicit definition, rather than describing it?
where $\Lambda^{eg}_{0,jk}$ is the electronic two photon transition moment between $g$ and $e$.\cite{McClain1977}
$\Lambda$ contains the summation over $m$ in \autoref{ABterms}.

\autoref{ABterms} shows the selection rules for the vibronic transitions.
The $A$ term is allowed whenever an electronic transition has a one- and two- photon transition moment.
The brightness is controlled by vibrational overlap (Franck-Condon factors).
For centrosymmetric molecules, however, an electronic transition cannot be both one- and two- photon allowed, so the $A$ term will vanish.\cite{Milojevich2013, RN230}
This makes HDFG a unique tool for studying the electronic structure of centrosymmetric species in isotropic media, as it is sensitive to non-Condon effects.\cite{Olson2018}
In the absence of an $A$ term, the $B$ terms will dominate.
The $B_1$ and $B_2$ terms involve different types of vibronic coupling pathways.
In $B_1$, the Herzberg-Teller coupling is associated with the two-photon absorption process, whereas in $B_2$, the Herzberg-Teller coupling is associated with one-photon emission.
As such, $B_1$ contributions to a HDFG spectrum will be sensitive to vibronic coupling between the ground state of a mode and vibrational states on the $|e)$ surface. 
$B_2$ contributions are sensitive to vibronic coupling between the first excited state of a mode $\ket{g,1}$ and vibrational states on $|e)$.

\begin{figure*}[!htbp]
	\centering
	\includegraphics[width=6.66in]{drsive_spectrum.png}
	\caption{Contributions of $A, B$ (\autoref{ABterms_DR}) to HDFG spectrum for a simple two harmonic well system.
		(a) Potential energy surfaces for a two-well system, (b) 1D HDFG spectrum for $\xi = 0.5$, $\omega_1 = \omega_{g1, g0}$. 
		It is assumed that $\omega_2 = \omega_3$.
		Note that (b) plots magnitudes of the labeled quantities.
		The vibrational states on the $|g)$ and $|e)$ manifolds are spaced 2200 cm$^{-1}$ apart, with the vibronic states $\ket{e,v'}$ given linewidths of 700 cm$^{-1}$ and $\hbar \omega_{eg}$ = 30000 cm$^{-1}$.
		Dotted lines in (b) denote the $v'$ = 0, 1, 2 vibronic resonances. 
		The vibronic one and two photon absorption operators are scaled such that $\abs{B}/\abs{A} \sim$ 0.1, following Chung and Ziegler. \cite{Ziegler1988}}
	\label{fig:doubres_spec}
\end{figure*}

The impact of vibronic coupling in the 2D spectrum is made clear by using a simple model. \cite{Kundu2022}
Using a two-well system described by 
\begin{subequations}
	\begin{equation}
		H_g = \frac{p^2}{2m} + \frac{1}{2} \hbar \omega q^2
	\end{equation}
and
	\begin{equation}
		H_e = \frac{p^2}{2m} + \frac{1}{2} \hbar \omega (q-\xi)^2 +\hbar \omega_{eg}
	\end{equation}
\end{subequations}
for the ground ($H_g$) and first excited ($H_e$) states, where $p$ is the momentum of the normal mode, the A and B contributions can be evaluated using Franck-Condon and Herzberg-Teller integrals tabulated in terms of the dimensionless normal mode $q$ and offset parameter $\xi$ (\autoref{fig:doubres_spec}a). \cite{Carlson1988thesis} 
Note that $q = \sqrt{\frac{m^2\omega}{\hbar}} Q$.
The spectrum is simulated for an electronic state which is both one and two photon allowed.
A simulated spectrum (\autoref{fig:doubres_spec}b) highlighting the contributions of these terms on potential wells with $\xi = 0.5$ dissects the $A$ and $B$ contributions to the HDFG spectrum.
This stimulated hyper-Raman type spectrum would be the expected result in a HDFG experiment when investigating the vibronic structure of the electronic state coupled to $\ket{g,v}$.

Simulating the HDFG spectrum for the simple two-well system allows dissection of selection rules and spectral signatures without the need for complex couplings.
There are two relevant regions of interest: the resonant region (2$\omega_2$ $\in$ [29000, 35000] cm$^{-1}$) and the non-resonant region.
Focusing far away from the resonant region ($2\omega_2 \sim$ 20000 cm$^{-1}$), the nonresonant $A$ term response is roughly equivalent to that of the resonant $B$ term response. 
Previous reports suggest that $A$ term contributions may become negligible when significantly detuned from a resonance such that $\Delta_{ev', g0} \approx \Delta_{eg}$, i.e., the resonance denominator loses $\ket{v'}$ dependence. \cite{Neddersen1989}
The lack of $\ket{v'}$ dependence in the resonance denominator causes $A$ to vanish through closure ($A_{ijk} \sim \sum_{v'} \langle 1|v' \rangle \langle v'|0\rangle$ = $\delta_{10} = 0$).
However, the simulated spectrum (\autoref{fig:doubres_spec}b) shows a non-negligible $A$ contribution to HDFG output well beyond $\sim$ 20000 cm$^{-1}$, the limit for this model system where $\abs{\omega_{ev',g0} - 2\omega_2} \gg 2\Gamma_{ev',g0}$.
As such, it is difficult to eliminate $A$ term resonances in HDFG spectra, even when largely detuned ($\gg 2\Gamma_{ev',g0}$) from the electronic state. 
Similar ideas have been seen in spontaneous Raman scattering. \cite{Li1990, Gong2015}
As such, it may prove difficult to examine non-Condon effects in HDFG spectra of noncentrosymmetric systems.

@@

\section{Comparisons with other spectroscopies}\label{quant}
\subsection{Site Selectivity}
Unlike resonant hyper-Raman spectroscopy, which allows transitions between different normal modes of varying quanta, the infrared pulse in the HDFG provides a type of site selectivity,\cite{RN103, Carlson1991} so that only the mode pumped by $\omega_1$ can be involved in vibronic coupling.  
% DDK: I kind of understand this point...but a hyper-Raman spectrum would clearly select the vibrational mode based on the Raman shift, correct?
%  good to note the benefits of this technique compared to hyper-Raman:
% - a form of stimulated hyper-Raman (=stronger, directional signals)
% - experiment takes place over a short time window, so pump-probe experiments are easily implemented
% - laser scatter is easily avoided
% - IR active, not 
HDFG methods can supplement other coherent Raman based methods as a method to investigate vibronic coupling mechanisms between a specific vibration on the ground state and vibrational states on an arbitrary excited state.\cite{RN103}
The combined infrared and hyper-Raman properties of HDFG make it highly sensitive to molecular electronic structure.
Particularly in the case of a centrosymmetric species, non-Condon effects dominate in the spectrum as the $A$ term vanishes from the presence of an inversion center.
The site selective properties of HDFG can allow for parsing of non-Condon effects in different vibrational modes, and extend the use of CMDS to understand the electronic and vibronic structure of simple and complex species.
